Kids PM Summary

### 2020-04-09 child_health_data_cleaning.Rmd
Update LRTI tracking

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 6 April 2020"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
wmt_csq_initial <- read_xlsx("Input/WMT/wmt_csq_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         csq_date = ymd(Date),
         csq_collect = as.character(HowCollected),
         csq_sick_2_weeks = as.character(Illin2Weeks),
         csq_still_sick = as.character(StillSick),
         csq_first_symptom_date = ymd(FirstSymptomDate),
         csq_symptom_free_date = ymd(SymptomFreeDate),
         csq_miss_work = as.character(MissWork),
         csq_miss_work_days = as.character(DaysMissed),
         csq_see_dr = as.character(SeeDr),
         csq_dr_diagnosis = as.character(DrDiagnosis),
         csq_new_meds = as.character(NewMeds),
         csq_fever_2weeks = as.character(Fever),
         csq_temp_2weeks = as.numeric(Temperature),
         csq_rapid_breathing_2weeks = as.character(RapidBreathing),
         csq_difficult_breathing_2weeks = as.character(DifficultBreathing),
         csq_noisy_breathing_2weeks = as.character(NoisyBreathing),
         csq_runny_nose_2weeks = as.character(RunnyNose),
         csq_cough_2weeks = as.character(Coughing),
         csq_wheeze_2weeks = as.character(Wheezing),
         csq_fever_current = as.character(FeverStill),
         csq_rapid_breathing_current = as.character(RapidBreathingStill),
         csq_difficult_breathing_current = as.character(DifficultBreathingStill),
         csq_noisy_breathing_current = as.character(NoisyBreathingStill),
         csq_runny_nose_current = as.character(RunnyNoseStill),
         csq_cough_current = as.character(CoughingStill),
         csq_wheeze_current = as.character(WheezingStill),
         csq_comments = as.character(Comments)) %>% 
  select(home_winter_id:csq_comments)

@@

>>>>

---
title: "Kids health and child data cleaning"
author: "Ethan Walker"
date: "Started 27 Feb 2020, Updated 8 April 2020"
output: pdf_document 
---

@@

# Load and merge files from different locations
```{r}
wmt_csq_initial <- read_xlsx("Input/WMT/wmt_csq_20200227.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         csq_date = ymd(Date),
         csq_collect = as.character(HowCollected),
         csq_sick_2_weeks = as.character(Illin2Weeks),
         csq_still_sick = as.character(StillSick),
         csq_first_symptom_date = ymd(FirstSymptomDate),
         csq_symptom_free_date = ymd(SymptomFreeDate),
         csq_miss_work = as.character(MissWork),
         csq_miss_work_days = as.character(DaysMissed),
         csq_see_dr = as.character(SeeDr),
         csq_dr_diagnosis = as.character(DrDiagnosis),
         csq_new_meds = as.character(NewMeds),
         csq_fever_2weeks = as.character(Fever),
         csq_temp_2weeks = as.numeric(Temperature),
         csq_rapid_breathing_2weeks = as.character(RapidBreathing),
         csq_difficult_breathing_2weeks = as.character(DifficultBreathing),
         csq_noisy_breathing_2weeks = as.character(NoisyBreathing),
         csq_runny_nose_2weeks = as.character(RunnyNose),
         csq_cough_2weeks = as.character(Coughing),
         csq_wheeze_2weeks = as.character(Wheezing),
         csq_fever_current = as.character(FeverStill),
         csq_rapid_breathing_current = as.character(RapidBreathingStill),
         csq_difficult_breathing_current = as.character(DifficultBreathingStill),
         csq_noisy_breathing_current = as.character(NoisyBreathingStill),
         csq_runny_nose_current = as.character(RunnyNoseStill),
         csq_cough_current = as.character(CoughingStill),
         csq_wheeze_current = as.character(WheezingStill),
         csq_comments = as.character(Comments)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-999, -99, -99.9, 999, 0)) %>% 
  select(home_winter_id:csq_comments)

@@

################# Confirmed LRTI ###############

# Load and merge files from different locations
```{r}
wmt_ari_initial <- read_xlsx("Input/WMT/wmt_ari_20200408.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         child_id_num = as.character(ChildID),
         area = "WMT",
         lrti_number = as.character(ARINum),
         lrti_basis = as.character(ARIBasis),
         lrti_start_date_final = ymd(ProfessionalStartDate),
         lrti_end_date_final = ymd(ProfessionalEndDate),
         lrti_professional_comments = as.character(ProfessionalComments)) %>% 
  select(home_winter_id:lrti_professional_comments)

# Combine logs from all areas
kids_lrti <- wmt_ari_initial %>% 
  left_join(kids_linked_ids, c("area", "home_winter_id"))

# write_rds(kids_lrti, "Output/kids_lrti.rds")

kids_lrti <- read_rds("Output/kids_lrti.rds")

### 2020-04-09 child_health_data_summary.Rmd
Update LRTI tracking

---
title: "Kids health and child data summary"
author: "Ethan Walker"
date: "Started 16 March 2020, Updated 16 March 2020"
output: 
  powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE,
                      fig.height = 5, fig.width = 7)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

kids_med_visit <- read_rds("Output/kids_med_visit.rds") %>% 
  group_by(area, home_winter_id, child_id_num, med_visit_date) %>% 
  distinct(med_visit_date, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(temp1 = if_else(temp1 < 90, 0, temp1)) %>% 
  mutate(temp2 = if_else(temp2 < 90, 0, temp2)) %>% 
  mutate(temp3 = if_else(temp3 < 90, 0, temp3)) %>% 
  mutate(sp02 = if_else(sp02 < 80, 0, sp02)) %>% 
  replace_with_na_all(condition = ~.x %in% c(-9999, -99, 0)) %>% 
  # gather 3 moisture samples to calculate average
  gather("sample", "value", c("temp1":"temp3")) %>% 
  arrange(home_winter_id, med_visit_date) %>% 
  group_by(area, home_winter_id, med_visit_date) %>% 
  mutate(temp_ave = mean(value, na.rm = TRUE)) %>% 
  # spread 3 moisture samples back to wide format
  group_by(area, home_winter_id, med_visit_date, temp_ave) %>% 
  spread(sample, value) %>% 
  ungroup()

```

```{r}
medvisit_plot <- kids_med_visit %>% 
  filter(winter_id == 1) %>% 
  select(area, resp_rate, heart_rate, sp02, hr_sp02, temp_ave) %>% 
  pivot_longer(cols = c("resp_rate":"temp_ave"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(area, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "resp_rate", "Respiratory rate", "breaths/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "heart_rate", "Heart rate", "beats/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "sp02", "Sp02", "%")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "hr_sp02", "Heart rate from Sp02", "beats/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "temp_ave", "Temperature", "Degrees F")
```

@@

```{r}
medvisit_plot <- kids_med_visit %>% 
  filter(winter_id == 1) %>% 
  select(area, med_visit_ari, lethargy, retractions, wheeze, stridor, 
         crackles, referred) %>% 
  pivot_longer(cols = c("med_visit_ari":"referred"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

@@

  medvisit_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  medvisit_plot

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_ari", "Med visit ARI", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "lethargy", "Lethargy", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "retractions", "Retractions", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "wheeze", "Wheeze", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "stridor", "Stridor", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "crackles", "Crackles", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "referred", "Referred", "count")
```

>>>>

---
title: "Kids health and child data summary"
author: "Ethan Walker"
date: "Started 16 March 2020, Updated 8 April 2020"
output: 
  powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, 
                      include = TRUE, warning = FALSE,
                      fig.height = 5, fig.width = 8)
```

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

@@

kids_med_visit <- read_rds("Output/kids_med_visit.rds") 
```

```{r}
medvisit_plot <- kids_med_visit %>% 
  filter(winter_id == 1) %>% 
  select(area, med_visit_resp_rate, med_visit_heart_rate, med_visit_sp02, 
         med_visit_hr_sp02, med_visit_mean_temp) %>% 
  pivot_longer(cols = c("med_visit_resp_rate":"med_visit_mean_temp"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot(aes(area, value)) +
    geom_boxplot(aes(size = 1), lwd = 1.2, colour = "black", 
               fatten = 1, outlier.size = 1.5, width = 0.35) +
    theme_minimal() +
    theme(strip.text = element_text(size = 14, colour = "black"),
          axis.text.x = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_resp_rate", "Respiratory rate", "breaths/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_heart_rate", "Heart rate", "beats/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_sp02", "Sp02", "%")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_hr_sp02", "Heart rate from Sp02", "beats/min")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_mean_temp", "Temperature", "Degrees F")
```

@@

```{r}
medvisit_plot <- kids_med_visit %>% 
  filter(winter_id == 1) %>% 
  select(area, med_visit_lethargy, med_visit_retractions, med_visit_wheeze, 
         med_visit_stridor, med_visit_crackles, med_visit_referred) %>% 
  pivot_longer(cols = c("med_visit_lethargy":"med_visit_referred"), names_to = "var") %>% 
  filter(!is.na(value)) %>% 
  ggplot() +
    geom_bar(aes(value, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 12, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    facet_wrap(~var, scales = "free_y")
medvisit_plot
```

@@

  medvisit_plot <- data %>% 
    filter(winter_id == 1) %>% 
    select(area, var) %>% 
    rename(plot_var = var) %>% 
    filter(!is.na(plot_var)) %>% 
    ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(strip.text = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          axis.text.x = element_text(size = 14, colour = "black", 
                                     angle = 25, vjust = 0.6),
          legend.text = element_text(size = 16, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = cbPalette)
  medvisit_plot

@@

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_lethargy", "Lethargy", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_retractions", "Retractions", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_wheeze", "Wheeze", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_stridor", "Stridor", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_crackles", "Crackles", "count")
```

@@

```{r}
medvisit_summary_function(kids_med_visit, "med_visit_referred", "Referred", "count")
```

### 2020-04-09 lrti_tracking.Rmd
Update LRTI tracking

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 7 April 2020"
output: pdf_document 
---

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_exposure_data_sampling_day %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         med_visit_date:med_visit_mean_temp,
         csq_date:csq_comments, 
         med_rec_visit_date, med_rec_dr_diagnosis, med_rec_ari, med_rec_comments) %>% 
  # Currently only have this data for WMT - need to get new files and updates dataset
  filter(area == "WMT") %>% 
  # This is the most broad way of distinguishing if a child was sick
  # Need to get Paul's protocol for diagnosis to filter down from here
  filter(csq_sick_2_weeks == "Yes")
```

@@

```{r}
# Further filtering and re-ordering of variables
lrti_diagnosis_data_filtered <- lrti_diagnosis_data %>% 
  select(area:med_visit_ari, csq_date:csq_symptom_free_date, 
         med_rec_visit_date:med_rec_comments, med_visit_lethargy:csq_comments) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, csq_collect) %>% 
  # If a home CSQ was done on same visit date as initial phone CSQ, filter for only the home CSQ
  distinct(csq_sick_2_weeks, .keep_all = TRUE) %>% 
  select(area:csq_still_sick, med_visit_referred, csq_see_dr, 
         csq_first_symptom_date:csq_comments) %>% 
  # Were they referred (med visit) or did they see a Dr (CSQ)?
  filter(med_visit_referred == "Yes" | csq_see_dr == "Yes") %>% 
  # If yes, did we get medical records?
  filter(!is.na(med_rec_visit_date)) %>% 
  # If yes, was there an ARI diagnosis?
  filter(med_rec_ari == "ARI" | med_rec_ari == "Possible ARI") %>% 
  group_by(child_id_num) %>% 
  distinct(med_rec_visit_date, .keep_all = TRUE)
```

@@

```{r}
# LRTI start date, end date, and at-risk period identification
lrti_data <- health_exposure_data_sampling_day %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         med_visit_date:med_visit_notes, chw_dr_relook:chw_ari_comments,
         csq_date:csq_comments, med_rec_visit_date:med_rec_comments) %>% 
  filter(area == "WMT") %>% 
  filter(csq_sick_2_weeks == "Yes") %>% 
  select(area:med_visit_ari, csq_date:csq_symptom_free_date, 
         med_rec_visit_date:med_rec_comments, med_visit_lethargy:csq_comments) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, csq_collect) %>% 
  distinct(csq_sick_2_weeks, .keep_all = TRUE) %>% 
  select(area:csq_still_sick, med_visit_referred, csq_see_dr, 
         csq_first_symptom_date:csq_comments)
  mutate(trash_date = ymd("2099-01-01"),
         still_sick_date = if_else(csq_still_sick == "Yes", csq_date, trash_date),
         med_rec_ari_date = if_else(med_rec_ari != "No ARI", med_rec_visit_date, trash_date),
         med_visit_ari_date = if_else(med_visit_ari != "No", med_visit_date, trash_date)) %>% 
  pivot_longer(cols = c("still_sick_date", "med_rec_ari_date", "med_visit_ari_date"),
               names_to = "lrti_visits", values_to = "lrti_dates") %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  mutate(lrti_start_date_new = if_else(!is.na(csq_first_symptom_date),
                                       csq_first_symptom_date, lrti_dates)) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         csq_first_symptom_date, lrti_start_date_new, lrti_visits, lrti_dates, trash_date,
         csq_sick_2_weeks, csq_still_sick, med_rec_ari, med_visit_ari) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, lrti_dates) %>% 
  distinct(visit_date, .keep_all = TRUE) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num) %>% 
  distinct(lrti_start_date_new, .keep_all = TRUE)

table(lrti_data$med_visit_ari)
table(health_exposure_data_sampling_day$csq_sick_2_weeks)
```

>>>>

---
title: "Kids LRTI tracking"
author: "Ethan Walker"
date: "Started 6 April 2020, Updated 8 April 2020"
output: pdf_document 
---

@@

```{r}
# LRTI Diagnosis data
lrti_diagnosis_data <- health_exposure_data_sampling_day %>% 
  # select relevant health data
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         med_visit_date:med_visit_mean_temp,
         csq_date:csq_comments, 
         med_rec_visit_date, med_rec_dr_diagnosis, med_rec_ari, med_rec_comments,
         lrti_number:lrti_professional_comments) %>% 
  # Currently only have this data for WMT - need to get new files and updates dataset
  filter(area == "WMT") %>% 
  # This is the most broad way of distinguishing if a child was sick
  # Need to get Paul's protocol for diagnosis to filter down from here
  filter(csq_sick_2_weeks == "Yes") 
```

@@

```{r}
# Further filtering and re-ordering of variables
lrti_diagnosis_data_filtered <- lrti_diagnosis_data %>% 
  select(area:med_visit_ari, csq_date:csq_symptom_free_date, 
         med_rec_visit_date:med_rec_comments, med_visit_lethargy:csq_comments,
         lrti_number:lrti_professional_comments) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, csq_collect) %>% 
  # If a home CSQ was done on same visit date as initial phone CSQ, filter for only the home CSQ
  distinct(csq_sick_2_weeks, .keep_all = TRUE) %>% 
  select(area:csq_still_sick, med_visit_referred, csq_see_dr, 
         csq_first_symptom_date:lrti_professional_comments) %>% 
  # Were they referred (med visit) or did they see a Dr (CSQ)?
  filter(med_visit_referred == "Yes" | csq_see_dr == "Yes") %>% 
  # If yes, did we get medical records?
  filter(!is.na(med_rec_visit_date)) %>% 
  # If yes, was there an ARI diagnosis?
  filter(med_rec_ari == "ARI" | med_rec_ari == "Possible ARI") %>% 
  group_by(child_id_num) %>% 
  distinct(med_rec_visit_date, .keep_all = TRUE)
```

@@

The initial attempt at having R select start dates did not match up well with
the cases in which Paul had already finalized the start/end dates. There seems
to be a good amount of professional opinion by assessing symptoms and medical
records. It may be best to filter a dataset down to only confirmed LRTI cases
and useful health/medical variables, then decide start/end/at-risk times 
on a case-by-case basis.

```{r}
# LRTI start date, end date, and at-risk period identification
lrti_date_data <- health_exposure_data_sampling_day %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         med_visit_date:med_visit_notes, chw_dr_relook:chw_ari_comments,
         csq_date:csq_comments, med_rec_visit_date:med_rec_comments,
         lrti_number:lrti_professional_comments) %>% 
  filter(area == "WMT") %>% 
  filter(csq_sick_2_weeks == "Yes") %>% 
  select(area:med_visit_ari, csq_date:csq_symptom_free_date, 
         med_rec_visit_date:med_rec_comments, 
         med_visit_lethargy:lrti_professional_comments) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, csq_collect) %>% 
  distinct(csq_sick_2_weeks, .keep_all = TRUE) %>% 
  select(area:csq_still_sick, med_visit_referred, csq_see_dr, 
         csq_first_symptom_date:lrti_professional_comments) %>% 
  mutate(trash_date = ymd("2099-01-01"),
         still_sick_date = if_else(csq_still_sick == "Yes", 
                                   csq_date, trash_date),
         med_rec_ari_date = if_else(!is.na(med_rec_visit_date), 
                                    med_rec_visit_date, trash_date),
         med_visit_ari_date = if_else(!is.na(med_visit_date), 
                                      med_visit_date, trash_date)) %>% 
  pivot_longer(cols = c("still_sick_date", "med_rec_ari_date", "med_visit_ari_date"),
               names_to = "lrti_visits", values_to = "lrti_dates") %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num, visit_date) %>% 
  mutate(lrti_start_date_new = if_else(!is.na(csq_first_symptom_date),
                                       csq_first_symptom_date, lrti_dates)) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         csq_first_symptom_date, lrti_start_date_new, lrti_visits, lrti_dates, trash_date,
         csq_sick_2_weeks, csq_still_sick, med_rec_ari, med_visit_ari,
         lrti_number:lrti_professional_comments) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, visit_date, lrti_dates) %>% 
  distinct(visit_date, .keep_all = TRUE) %>% 
  group_by(area, home, home_winter_id, winter_id, child_id_num) %>% 
  distinct(lrti_start_date_new, .keep_all = TRUE) %>% 
  distinct(child_id_num, lrti_number, .keep_all = TRUE) %>% 
  filter(!is.na(lrti_number)) %>% 
  select(child_id_num, home_winter_id, lrti_number, lrti_start_date_new:lrti_dates, 
         lrti_start_date_final, lrti_end_date_final, area:lrti_professional_comments)
```

### 2020-04-09 merge_health_datasets.Rmd
Update LRTI tracking

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 7 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
at_home_pm_merged <- read_rds("Output/at_home_pm_merged.rds")
kids_med_visit <- read_rds("Output/kids_med_visit.rds")
kids_birth_infancy <- read_rds("Output/kids_birth_infancy.rds")
child_home_winter <- read_rds("Output/child_home_winter.rds")
kids_csq <- read_rds("Output/kids_csq.rds")
kids_medical_records <- read_rds("Output/kids_medical_records.rds")
```

@@

#write_rds(health_merged5, "Output/health_data_merged.rds")
#write_csv(health_merged5, "Output/health_data_merged.csv")
```

>>>>

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 8 April 2020"
output: pdf_document
---

@@

# Load individual datasets
```{r}
at_home_pm_merged <- read_rds("Output/at_home_pm_merged.rds")
kids_med_visit <- read_rds("Output/kids_med_visit.rds")
kids_birth_infancy <- read_rds("Output/kids_birth_infancy.rds")
child_home_winter <- read_rds("Output/child_home_winter.rds")
kids_csq <- read_rds("Output/kids_csq.rds")
kids_lrti <- read_rds("Output/kids_lrti.rds")
kids_medical_records <- read_rds("Output/kids_medical_records.rds")
```

@@

kids_lrti <- read_rds("Output/kids_lrti.rds") %>% 
  select(-home_id)

health_merged6 <- health_merged5 %>% 
  left_join(kids_lrti, by = c("area", "home", "home_winter_id", "winter_id", 
                                      "child_id_num", "treatment")) %>% 
  arrange(area, home, home_winter_id, winter_id, child_id_num, sample_date) %>% 
  select(area, home, home_winter_id, winter_id, child_id_num, visit_date,
         treatment, sample_date, sampling_day, at_home_location, 
         pm_at_home_sampling_day, pm_at_home_sampling_period, csq_date:lrti_professional_comments) %>% 
  ungroup()

#write_rds(health_merged6, "Output/health_data_merged.rds")
#write_csv(health_merged6, "Output/health_data_merged.csv")
```

### 2020-04-09 pm_summary.Rmd
Update LRTI tracking

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 16 March 2020"
output: powerpoint_presentation
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(knitr)
library(lubridate)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = mean(pm, na.rm = TRUE), 
            "SD PM" = sd(pm, na.rm = TRUE),
            "Min PM" = min(pm, na.rm = TRUE), 
            "25%" = quantile(pm, 0.25, na.rm = TRUE),
            "Median PM" = median(pm, na.rm = TRUE),
            "75%" = quantile(pm, 0.75, na.rm = TRUE),
            "Max PM" = max(pm, na.rm = TRUE),
            "Mean Sample Days" = mean(pm_sample_interval, na.rm = TRUE),
            "SD Sample Days" = sd(pm_sample_interval, na.rm = TRUE),
            "Mean Sample Obs" = mean(pm_total_observations, na.rm = TRUE),
            "Mean % Daily Obs" = mean(percent_daily_obs_pm, na.rm = TRUE)) %>% 
  #select(-treatment) %>% 
  t()

kable(pm_summary, 
      digits = 1, align = "c")

>>>>

---
title: "Kids PM Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated Apri 8 2020"
output: powerpoint_presentation
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readr)
library(readxl)
library(knitr)
library(lubridate)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", 
               "#0072B2", "#D55E00", "#CC79A7")
```

@@

# Summary stats
```{r}
pm_summary <- pm_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(pm < 500) %>% 
  mutate(pm = if_else(pm > 500, 500, pm)) %>% 
  group_by(area) %>% 
  summarize("n" = n(),
            "Mean PM" = round(mean(pm, na.rm = TRUE)), 
            "SD PM" = round(sd(pm, na.rm = TRUE)),
            "Min PM" = round(min(pm, na.rm = TRUE)), 
            "25%" = round(quantile(pm, 0.25, na.rm = TRUE)),
            "Median PM" = round(median(pm, na.rm = TRUE)),
            "75%" = round(quantile(pm, 0.75, na.rm = TRUE)),
            "Max PM" = round(max(pm, na.rm = TRUE)),
            "Mean Sample Days" = round(mean(pm_sample_interval, na.rm = TRUE)),
            "SD Sample Days" = round(sd(pm_sample_interval, na.rm = TRUE))) %>% 
  #select(-treatment) %>% 
  t()

kable(pm_summary, align = "c")
